\documentclass[12pt, a4paper]{article}

\title{MATH2210 Fall 2023 Problem Sheet Week 9}
\author{Benjamin G. Thompson}
\date{November 1, 2023}

\usepackage[left=2cm, right=2cm, top=2cm, bottom=2cm]{geometry}
\usepackage{fancyhdr, amsmath}
\pagestyle{fancy}

\fancyhf{}
\lhead{MATH2210}
\chead{Week 11-W}
\rhead{November 1, 2023}
\cfoot{}

\begin{document}
Theorem 5.6.1 in the course notes is quite confusing on a first read. Let's work through some examples to get a better understanding of it.
\subsection*{Question 1a}
Let $T : R^2 \rightarrow R^2$ be the linear transformation which projects points in the plane to the y-axis. Let
\[
b = \begin{bmatrix}
  1 \\
  1 \\
  \end{bmatrix}.
\]

\begin{enumerate}
\item What is the matrix $A$ corresponding to $T$ (using the standard basis of $R^2$)?
\item Geometrically, describe the set of vectors $\{ b - Av : v \in R^2\}$.
\item Geometrically, what is the smallest possible value of $||b - Av||$?
  \item Give a geometric description of vectors $v$ which attain the minimum possible value above.
\end{enumerate}

\subsection*{Question 1b}
Let
\[
A = \begin{bmatrix}
  0 & 0 \\
  0 & 1 \\
  \end{bmatrix}, \quad 
b = \begin{bmatrix}
  1 \\
  1 \\
  \end{bmatrix}.
\]
\begin{enumerate}
\item Is the equation Av = b consistent?
\item What is the normal equation in $z$ corresponding to $Av = b$?
\item Substitute $A, b$ into the normal equation in the previous step, and solve for $z$.
  \item How do your $z$ values correspond to your geometric description in Question 1a?
\end{enumerate}

Let's now apply Theorem 5.6.1 to calculate the distance between a point and a plane.
\subsection*{Question 2}
  Consider the linear transformation  $T : R^2 \rightarrow R^3$ given by matrix
\[
A = \begin{bmatrix}
  1  & 0 \\
  0  & 1 \\
  -1 & -1 \\
\end{bmatrix},
\]
and let
\[
b = \begin{bmatrix}
  1 \\
  1 \\
  1 \\
  \end{bmatrix}.
\]
\begin{enumerate}
\item What is the equation of the plane given by Im$A$?
\item Geometrically, what is the closest point to $b$ on the plane? 
\item Is the equation $Ax = b$ consistent?
\item What is the normal equation in $z$ corresponding to this equation?
\item Solve the normal equation for $z$.
\item What is the value of $Az$? Is this value what you expected?
\end{enumerate}

\subsection*{Question 3}
Let $(a,b), (c,d)$ be two points in $R^2$ with $a \ne c$, and let
\[
A = \begin{bmatrix}
  1 & a \\
  1 & c \\
\end{bmatrix},
\quad
q = 
\begin{bmatrix}
  b \\
  d \\
\end{bmatrix}.
\]
\begin{enumerate}
\item What is the normal equation corresponding to $Ax = q$?
\item Solve the normal equation above.
\item What is the equation of the line through $(a,b)$ and $(c,d)$?
  \item How is the line you found above related to your solutions of the normal equation?
  \end{enumerate}
\end{document}
