\documentclass[12pt, a4paper]{article}

\title{MATH2210 Fall 2023 Problem Sheet Week 12}
\author{Benjamin G. Thompson}
\date{November 8, 2023}

\usepackage[left=2cm, right=2cm, top=2cm, bottom=2cm]{geometry}
\usepackage{fancyhdr, amsmath}
\pagestyle{fancy}

\fancyhf{}
\lhead{MATH2210}
\chead{Week 12-W}
\rhead{November 8, 2023}
\cfoot{}

\begin{document}
\noindent Let's revise some of the course content so far to help prepare for the prelim tomorrow.
\subsection*{Question 1}
What is an example of a $2 \times 2$ matrix which is:
\begin{enumerate}
\item not invertible and not diagonalizable?
\item not invertible but diagonalizable?
\item invertible but not diagonalizable?
\item invertible and diagonalizable?
\end{enumerate}

\subsection*{Question 2}
Let $U$ be the set of all points in 3-dimensional Euclidean space that lie in the $xy$ plane or the $xz$ plane. Prove or disprove the following statement: $U$ is a subspace of 3-dimensional Euclidean space.

\subsection*{Question 3}
Consider the following vectors:

\[
 \alpha_1 = \begin{bmatrix}
  1 \\
  2 \\
  3 \\
  4 \\
\end{bmatrix},
\quad
\alpha_2 = \begin{bmatrix}
  2 \\
  3 \\
  4 \\
  1 \\
\end{bmatrix},
\quad
\alpha_3 = \begin{bmatrix}
  3 \\
  4 \\
  1 \\
  2 \\
\end{bmatrix},
\quad
\alpha_4 = \begin{bmatrix}
  4 \\
  1 \\
  2 \\
  3 \\
\end{bmatrix}
\]
\begin{enumerate}
\item Is the set $\{ \alpha_1, \alpha_2, \alpha_3, \alpha_4 \}$ a basis for 4-dimensional Euclidean space?
\item Can the vector
  \[
  \beta = \begin{bmatrix}
  1 \\
  1 \\
  1 \\
  1 \\
\end{bmatrix}
  \]
  be expressed an a linear combination of $\alpha_1,\alpha_2,\alpha_3,\alpha_4$? If so, provide such an expression. If not, prove it is impossible to do so.
\end{enumerate}

  

\subsection*{Question 4}
Consider the plane in 3-dimensional Euclidean space given by the equation $x + 2y + 3z = 0$.
\begin{enumerate}
\item What is a $3 \times 3$ matrix whose null space is this plane?
\item What is a $3 \times 3$ matrix whose column space is this plane?
 \end{enumerate} 



\subsection*{Question 5}
Let $A,B,C$ be $2 \times 2$ matrices, and let $\text{tr}$ denote the trace of a matrix. Are the following true or false? Justify your answers.
\begin{enumerate}
\item $\text{tr}(ABC) = \text{tr}(CBA)$
  \item $\text{tr}(ABC) = \text{tr}(BCA)$
  \end{enumerate}

\end{document}
